### 2009-11-05 doc/tech_doc/a-rex/arex_tech_doc.tex
Explicitly stating that reference is pointing to a section.
improvements to the cache section after feedback from Martin Skou

The A-REX can cache input files. Caching is enabled if one or more
cache directories are specified in the configuration file. Caching can
also be explicitly turned off by the user for each file by using
the\textit{ cache=no} option in the URL (for URL options read
{}``Protocols, Uniform Resource Locators (URL) and extensions
supported in ARC'' \cite{urls}). The disk space occupied by the cache
is controlled by removing old files.  For more information on
configuration look in section \ref{SubSection:ConfigFile}.

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which the notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finished (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7 days for \emph{ttl} and 30 days for \emph{ttr}.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by usingon
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to the directory
in which the SD is created. If the path is {*} the default one is
used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} - specifies
a directory to store cached data (see \ref{sec:cache}). Multiple
cache directories may be specified by specifying multiple \emph{cachedir}
commands. Cached files will be distributed evenly between the caches.
Specifying no \emph{cachedir }command or commands with an empty path
disables caching. Optional \textit{link\_path} specifies the path
at which \emph{path} is accessible on computing nodes, if it is different
from the path on the A-REX host. If \textit{link\_path} is set to '.'
files are not soft-linked, nor are per-job links created, but files
are copied to the session directory.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} - specifies
high and low watermarks for space used by each cache, as a percentage
of the space on the file system on which the cache directory is located.
When the max is exceeded, files will be deleted to bring the used
space down to the min level. It is a good idea to have each cache
on its own separate file system. To turn off this feature, \char`\"{}cachesize\char`\"{}
without parameters can be specified. These cache settings apply to
all caches specified by \emph{cachedir} commands.
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. Actual
number is provided in job description and defaults to 0.
\end{itemize}

>>>>

The A-REX can cache input files, so that subsequent jobs requiring the
same files do not have to download them again. Caching is enabled if
one or more cache directories are specified in the configuration
file. All input files except files uploaded by the user during job
submission are cached by default. This includes excutable files
downloaded by the A-REX. Caching can be explicitly turned off by the
user in the job description (see~\cite{userguide1}). The disk space
occupied by the cache is controlled by removing files in the order of
least recent access. For more information on configuration see
Section~\ref{SubSection:ConfigFile}.

@@

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which the notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finished (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7 days for \emph{ttl} and 30 days for \emph{ttr}.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by usingon
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to the directory
in which the SD is created. If the path is {*} the default one is
used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} - specifies
a directory to store cached data (see section \ref{sec:cache}). Multiple
cache directories may be specified by specifying multiple \emph{cachedir}
commands. Cached files will be distributed evenly between the caches.
Specifying no \emph{cachedir }command or commands with an empty path
disables caching. Optional \textit{link\_path} specifies the path
at which \emph{path} is accessible on computing nodes, if it is different
from the path on the A-REX host. If \textit{link\_path} is set to '.'
files are not soft-linked, nor are per-job links created, but files
are copied to the session directory.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} - specifies
high and low watermarks for space used by each cache, as a percentage
of the space on the file system on which the cache directory is located.
When the max is exceeded, files will be deleted to bring the used
space down to the min level. It is a good idea to have each cache
on its own separate file system. To turn off this feature, \char`\"{}cachesize\char`\"{}
without parameters can be specified. These cache settings apply to
all caches specified by \emph{cachedir} commands.
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. Actual
number is provided in job description and defaults to 0.
\end{itemize}
